Towards Transparency and Open Science

### 2023-02-06 manuscript.Rmd
found a can not
passive

Transparency is necessary because induction leaves researchers overly optimistic regarding their theories' fit to the data ($\mathcal{C}$).
The extent of this optimism depends on the inductive process, not merely its results.
Specifically, it depends on the complexity, i.e., the ability of the inductive process to adapt to data.
The ability to adapt to data is independent of the specific data that was observed.
Complexity is a function of the model, i.e., $\mathcal{C}(\text{model})$, not of the data.
Without knowing the inductive process, researchers can not judge the overconfidence, so the inductive process ought to be made transparent.

@@

The above sections aimed to motivate the observation that the apparent fit of a theory to data is often overly optimistic if it has inductive elements.
This observation is only useful if we know the extent of this optimism.
However, both setups show that the extent of the optimism is closely related to the complexity of the inductive process ($\mathcal{C}(\text{model})$) and give us two starting points for making this bias transparent.
The first requires a formal analysis of the inductive process to compute the complexity (e.g., using information criteria), and the second merely requires that the process is repeatable (e.g., using cross-validation).
Both approaches require researchers to make the inductive process transparent instead of merely publishing the results.

>>>>

Transparency is necessary because induction leaves researchers overly optimistic regarding their theories' fit to the data ($\mathcal{C}$).
The extent of this optimism depends on the inductive process, not merely its results.
Specifically, it depends on the complexity, i.e., the ability of the inductive process to adapt to data.
The ability to adapt to data is independent of the specific data that was observed.
Complexity is a function of the model, i.e., $\mathcal{C}(\text{model})$, not of the data.
Without knowing the inductive process, researchers cannot judge the overconfidence, so the inductive process ought to be made transparent.

@@

The above sections aimed to motivate the observation that the apparent fit of a theory to data is often overly optimistic if it has inductive elements.
This observation is only useful if we know the extent of this optimism.
However, both setups show that the extent of the optimism is closely related to the complexity of the inductive process ($\mathcal{C}(\text{model})$) and suggest two starting points for making this bias transparent.
The first requires a formal analysis of the inductive process to compute the complexity (e.g., using information criteria), and the second merely requires that the process is repeatable (e.g., using cross-validation).
Both approaches require researchers to make the inductive process transparent instead of merely publishing the results.
